---
title: "613FinalPJ"
author: "Ting Yi Chuang, Yen Chun Lin"
date: "2024-04-11"
output: html_document
---


```{r}
library(tidyverse)
customer_data <- read_csv("customer_data.csv")
customer_data_tbl <- as_tibble(customer_data)
dim(customer_data)
head(customer_data)
head(customer_data_tbl)
summary(customer_data)
str(customer_data_tbl)
```


```{r}
customer_data_tbl <- customer_data_tbl %>%
  mutate(
    gender = as.factor(gender),
    education = as.factor(education),
    region = as.factor(region),
    loyalty_status = as.factor(loyalty_status),
    purchase_frequency = as.factor(purchase_frequency),
    product_category = as.factor(product_category),
    promotion_usage = as.factor(promotion_usage)
  )

str(customer_data_tbl)
```


```{r}
customer_data_tbl %>%
  summarise(
    average_age = mean(age, na.rm = TRUE),
    median_income = median(income, na.rm = TRUE),
    average_purchaseamount = mean(purchase_amount, na.rm = TRUE)
  )

customer_data_tbl %>%
  count(gender)

customer_data_tbl %>%
  group_by(education) %>%
  summarise(average_income = mean(income, na.rm = TRUE))
```


```{r}
library(ggplot2)
# Plotting income distribution by gender
ggplot(customer_data_tbl, aes(x = income, fill = gender)) +
  geom_histogram(bins=10, alpha=0.7, color="black") +
  labs(title = "Income Distribution by Gender",
       x = "Income", 
       y = "Count") +
  theme_minimal()

# Satisfaction score by loyalty status
ggplot(customer_data_tbl, aes(x = loyalty_status, y = satisfaction_score, fill = loyalty_status)) +
  geom_boxplot() +
  labs(title = "Customer Satisfaction by Loyalty Status", 
       x = "Loyalty Status", 
       y = "Satisfaction Score") +
  theme_minimal()

# Plotting purchase amounts by product category
ggplot(customer_data_tbl, aes(x = product_category, y = purchase_amount, fill = product_category)) +
  geom_boxplot() +
  labs(title = "Purchase Amount by Product Category", 
       x = "Product Category", 
       y = "Purchase Amount")

```


```{r}
library(data.table)
customer <- fread("customer_data.csv")
dim(customer)
typeof(customer)
str(customer)
customer[, .(id, age, gender, education, region)]
```


```{r}
customer_master<-customer[education=="Masters"]
customer_master
customer_master[, .(gender, income, purchase_amount)][income >27516.27 & purchase_amount > 9634.791 & gender == "Female"]
```


- $H_0: There is no difference in satisfaction scores between different loyalty status groups.$

- $H_a: There is a difference in satisfaction scores between different loyalty status groups.$

```{r}
anova_result <- aov(satisfaction_score ~ loyalty_status, data = customer_data_tbl)
summary(anova_result)
```
- $H_0: There is no relationship between income and the purchase amount of customers.$

- $H_a: Higher income customers spend more on purchases than lower income customers.$

```{r}
anova_result1 <- aov(income ~ purchase_amount, data = customer_data_tbl)
summary(anova_result1)
```


- $H_0: The product category does not influence the average purchase amount..$

- $H_a: The product category influences the average purchase amount.$

```{r}
anova_result2 <- aov(purchase_amount ~ product_category, data = customer_data_tbl)
summary(anova_result2)
```





